\documentclass{beamer}
\usepackage{enumerate}
\author{\hspace{0.285cm}Student Name : Tan Chong Raen\\Student ID : 1121115725}
\title{Data Mining and Data Warehouse}
\institute{Multimedia University\\(Cyberjaya Campus)}
\date{\today}
\usetheme{Rochester}

\begin{document}

\maketitle

\begin{frame}
\section{Introduction and Problem statement}
\frametitle{Introduction and Problem statement}
\large \textbf{\underline{Introduction}}
\begin{itemize}
\item \textit{Data Mining} : a technique used to discover the meaningful and valuable information from a massive of data and covert it into the knowledge of someone or something behavior.
\end{itemize}
\large \textbf{\underline{Problem statement}}
\begin{itemize}
\item Amount of time and cost used for discovery of patterns of data.
\item Need to study a massive of data to predict the response of customer.
\end{itemize}
\end{frame}

\begin{frame}
\section{Research method}
\frametitle{Research method}
\begin{itemize}
\item Theoretical work
\item Approaches(Use in data mining):
\begin{enumerate}[i.]
\item Verification Driven (most common)
\item Discovery Driven (most complicated)
\end{enumerate}
\item Six phases(Build a data mining project):
\begin{enumerate}[i.]
\item Problem Definition
\item Data Exploration
\item Date Preparation
\item Modeling
\item Evaluation
\item Deployment
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\section{Critical literature review}
\frametitle{Critical literature review}
\begin{itemize}
\item[] \textbf{\underline{Operations associated with Data Mining}} \\
\begin{enumerate}[i.]
\item \textit{Verification Driven}
\begin{enumerate}[a)]
\item Multidimensional analysis
\item Query and reporting
\item Statistical analysis
\end{enumerate}
\item \textit{Discovery Driven}
\begin{enumerate}[a)]
\item Predictive modeling
\item Deviation detection
\item Link analysis
\item Database Segmentation
\end{enumerate}
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\section{Conclusion}
\frametitle{Conclusion}
\begin{itemize}
\item \textit{Data mining} is more accuracy and efficiency.
\item \textit{Data mining} may provide the wrong information.
\item \textit{Internet} and \textit{Data Warehousing} is more important. 
\end{itemize}
\end{frame}

\begin{frame}
\section{What did we learn? Possible extension or Future work?}
\frametitle{What did we learn? Possible extension or Future work?}
\begin{itemize}
\item[] \large \textbf{\underline{What did we learn?}} \\
In this research assignment, we learn that the process of a completed data mining project and the advantages of data mining.
\item[]
\item[] \large \textbf{\underline{Possible extension or Future work?}}
\begin{enumerate}[i.]
\item Social media (Facebook, Twitter and so on)
\item Bioinformatics
\item Education
\end{enumerate}
\end{itemize}
\end{frame}

\end{document}